Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-06 tex/MesnardoBarba2019.tex
Mention Docker images built for Azure
Change "anyone" to "the reader"

\noindent Anyone can now pull the application image from DockerHub, and create a Docker container to run the CFD application software in a faithfully reproduced local environment.
Our objective is to create and run containers on the public cloud provider Microsoft Azure, and make it possible for the readers to also run these containers to reproduce our results.
Figure \ref{fig:cloud_workflow} shows a graphical representation of the workflow we developed using Docker and various tools for running CFD simulations on Microsoft Azure.
The next section explains these tools.

@@

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distributed GPU devices using the NVIDIA AmgX library.
Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

>>>>

\noindent A reader interested in reproducing the computational results can now pull the application image from DockerHub, and create a Docker container to run the CFD application software in a faithfully reproduced local environment.
Our objective is to create and run containers on the public cloud provider Microsoft Azure, and make it possible for the readers to also run these containers to reproduce our results.
Figure \ref{fig:cloud_workflow} shows a graphical representation of the workflow we developed using Docker and various tools for running CFD simulations on Microsoft Azure.
The next section explains these tools.

@@

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distributed GPU devices using the NVIDIA AmgX library.
Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
The Docker images were specifically built to be able to run MPI applications on RDMA-capable virtual machines (such as the NC24r instance with a CentOS-based 7.3 HPC image) with multiple-instance tasks on Azure Batch service.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
